%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Co-founder and CEO} % Job title
    {My Star Maps} % Organization
    {Edinburgh} % Location
    {Aug 2019 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Start-up selling personalised items with custom star maps.}
        \item {Design of the products and media using Adobe Photoshop, \textsc{Python}.}
        \item {Design and implementation of the website using Shopify.}
      \end{cvitems}
    }

  \cventry
    {Online advertising strategy and deployment} % Job title
    {Greaterskies} % Organization
    {Cambridge} % Location
    {October 2018 - November 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed a successful Facebook advertising strategy for Greaterskies.}
        \item {Designed the ad creatives using Adobe Photoshop.}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Full-stack developer} % Job title
    {The Star Maps} % Organization
    {Cambridge, UK} % Location
    {May 2018 - September 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Built an application for businesses to make their own star map designs.
        \item Used \textsc{Django} to handle the back-end and user management.
        \item Used \textsc{Javascript} and \textsc{JQuery} to build the interactive portal to make new designs.
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Code Reviewer} % Job title
    {Udacity} % Organization
    {} % Location
    { 2015-Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Review work submitted by students of Udacity's Nanodegree programs (code review, documentation review, styling, etc...).} 
        \item {Review \textsc{Python}, \textsc{HTML}, \textsc{CSS} and \textsc{Javascript}}
        \item {Kept a consistent rating by students of more than 4.7 out of 5.}
      \end{cvitems}
    }
%---------------------------------------------------------
  
  \cventry
    {Intern Software Engineer} % Job title
    {Xaar} % Organization
    {Cambridge, UK} % Location
    {July 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Wrote \textsc{Python} code to make a heat-map of ink-flow on print-heads.}
        \item {My code was successfully tested on commercial print-heads and moved to production.}
      \end{cvitems}
    }

\end{cventries}
