%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Research Assistant} % Job title
    {Chapman Rinker} % Organization
    {9401 Jeronimo Rd, Irvine, CA 92618} % Location
    {Nov 2017 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked with Professor Soangra and developed tools for physical therapy. This work focused on providing treatment through the use of and design of embedded devices. Provides non-invasive intervention methods as an alternative means of treatment.}
        \item {Built custom board around an AVR micro-controller and flashed it with custom AVR code along with custom layout to interface with embedded components and sensors}
        \item {Designed a PCB in kicad and had the final board manufactured from a fab facility. This is a miniaturization of the original stack of boards.}
         \item {Developed QT app for data collection for Mbient sensors.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Full-stack developer} % Job title
    {The Star Maps} % Organization
    {Cambridge, UK} % Location
    {May 2018 - September 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Built an application for businesses to make their own star map designs.
        \item Used \textsc{Django} to handle the back-end and user management.
        \item Used \textsc{Javascript} and \textsc{JQuery} to build the interactive portal to make new designs.
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Code Reviewer} % Job title
    {Udacity} % Organization
    {} % Location
    { 2015-Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Review work submitted by students of Udacity's Nanodegree programs (code review, documentation review, styling, etc...).} 
        \item {Review \textsc{Python}, \textsc{HTML}, \textsc{CSS} and \textsc{Javascript}}
        \item {Kept a consistent rating by students of more than 4.7 out of 5.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Intern Software Engineer} % Job title
    {Xaar} % Organization
    {Cambridge, UK} % Location
    {July 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Wrote \textsc{Python} code to make a heat-map of ink-flow on print-heads.}
        \item {My code was successfully tested on commercial print-heads and moved to production.}
      \end{cvitems}
    }

\end{cventries}
